---
title: "Ulrik Lyngs: CV"
---


<!-- add a floating table of contents: https://afeld.github.io/bootstrap-toc/ -->
<div class="row cv-page">
<!-- sidebar, which will move to the top on a small screen -->
<div class="col-sm-2">
<nav id="toc" data-toggle="toc" class="sticky-top"></nav>
</div>

<div class="col-sm-10">

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(knitr)
library(here)

#### publications #####
publications <- readxl::read_xlsx(here("_data", "publications.xlsx"))

#### all other entries #####
cv_entries <- readxl::read_xlsx(here("_data", "cv_entries.xlsx"))

```

# Summary

I am passionate about using insights from the behavioural neurosciences to **design digital technology that is sensitive to human limitations and biases**, particularly in relation to attention and self-regulation.

My **academic and professional background** is highly interdisciplinary, and I try to integrate best practices from many work spheres, such as using tools from large-scale event management to structure academic projects.

My **personal interests** include travelling & couchsurfing, samatha meditation, dancing (Cuban salsa and swing), and playing music (often with my concept band the [Karaoke Collective](https://karaokecollective.com)).

Download a brief version of [my CV as PDF](/pdfs/2020_lyngs_cv_brief.pdf).

# Academia {.domain-header}
## Education
```{r}
cv_entries %>% 
  filter(type == 'education') %>% 
  mutate(what = str_c(what, ", ", where)) %>% 
  mutate(year = str_c(year_begin, " --- ", year_end)) %>% 
  select(year, what) %>% 
  kable()
```


## Research
### Publications
```{r}
publications_table <- publications %>%
  arrange(desc(year), type) %>%
  mutate(author_year = str_c(authors_full, " (", year, "). ")) %>%
  #mutate(author_year = str_c("*", authors, " (", year, ")*. ")) %>%  #italicise authors and year
  mutate(title = ifelse(!is.na(url), str_c("[", title, "](", url, ")"), title)) %>% #turn title into link
  #mutate(title = str_c("<span style='text-decoration: underline'>", title, "</span>")) %>% #underline title
  mutate(citation = ifelse(!is.na(award),
                           str_c(author_year, title, venue, "<i class='fas fa-award'></i><em>", award, "</em>", sep = " "),
                           str_c(author_year, title, venue, sep = " "))) %>%
  mutate(citation = str_replace(citation, "Ulrik Lyngs", "_Ulrik Lyngs_")) %>%  # make my name italicised
  filter(type != "master's thesis") %>%
  select(type, citation)


publications_table %>%
  knitr::kable()

# library(DT)
# publications_table %>% 
#   datatable(rownames = FALSE, escape = FALSE, class = 'row-border', options = list(
#   pageLength = 10
# ))

```


### Talks
```{r, message=FALSE, warning=FALSE}
library(lubridate)
library(DT)
talks_table <- cv_entries %>% 
  filter(type == 'talk') %>% 
  mutate(where = str_replace(where, "\\[([^]]*)\\]\\(([^\\s^\\)]*)[\\s\\)]", "<a href='\\2'>\\1</a>")) %>% 
  mutate(what = str_c("<em>", what, "</em>, ", where)) %>% 
  #select(Year = year_begin, Talk = what) %>%
  select(Date = date, Talk = what) %>% 
  mutate(Date = as_date(Date)) %>% 
  arrange(desc(Date)) %>% 
  mutate(Date = str_c(year(Date),
                      ", ",
                      month(Date, label = TRUE)))
  
# DT library doesn't seem to be working
#talks_table %>% 
  #datatable(rownames = FALSE, escape = FALSE, class = 'row-border', options = list(pageLength = 10))

talks_table %>% 
  kable()

# cv_entries %>% 
#   filter(type == 'talk') %>% 
#   mutate(what = str_c("*", what, "*, ", where)) %>% 
#   select(year_begin, what) %>% 
#   kable()
  
  
```


### Posters
```{r}
cv_entries %>% 
  filter(type == 'poster') %>%
  mutate(what = str_c("*", what, "*, ", where)) %>% 
  select(year_begin, what) %>% 
  arrange(desc(year_begin)) %>% 
  kable()
```


## Teaching experience
```{r}
cv_entries %>% 
  filter(type == 'teaching') %>% 
  mutate(what = ifelse(!is.na(additional_info), 
    str_c("<span class='work-title'>", what, "</span><br class='work-break'>", where, "<br>", additional_info),
    str_c("<span class='work-title'>", what, "</span><br class='work-break'>", where))) %>% 
  mutate(year = ifelse(!is.na(year_end), str_c(year_begin, " --- ", year_end), year_begin)) %>% 
  select(year, what) %>% 
  kable()
```

## Other
### Grants and Awards
```{r}
cv_entries %>% 
  filter(type == 'grants_and_awards') %>% 
  mutate(what = str_c(what, ", ", where)) %>% 
  select(year_begin, what) %>% 
  kable()

```


### Media coverage
```{r}
cv_entries %>% 
  filter(type == 'media') %>%
  select(year_begin, what) %>% 
  kable()
```

### Service
```{r}
cv_entries %>% 
  filter(type == 'service') %>% 
  mutate(year_end = ifelse(year_end == "present", "", year_end)) %>%
  mutate(where = ifelse(!is.na(url), str_c("[", where, "](", url, ")"), where)) %>% 
  mutate(what = ifelse(!is.na(additional_info),
                       str_c(what,
                      "<br class='work-break'>", 
                      where),
                      str_c(what,
                      "<br class='work-break'>", 
                      where))) %>% 
  mutate(year = ifelse(!is.na(year_end), 
                       str_c(year_begin, " --- ", year_end),
                       year_begin)) %>% 
  select(year, what) %>% 
  kable()

```


# Work
## Selected employments
```{r}
cv_entries %>% 
  filter(type == 'work', is.na(website)) %>% 
  mutate(additional_info = replace_na(additional_info, "")) %>% 
  mutate(what = str_c("<span class='work-title'>", what, "</span><br class='work-break'>", where, "<br>", additional_info)) %>% 
  arrange(desc(year_begin)) %>% 
  mutate(year = ifelse(!is.na(year_end), str_c(year_begin, " --- ", year_end), year_begin)) %>% 
  select(year, what) %>% 
  kable()
```

## Professional development
```{r}
cv_entries %>% 
  filter(type == 'prof-dev') %>% 
  mutate(what = str_c(what, ", ", where)) %>% 
  select(year_begin, what) %>% 
  kable()
```

# Technical
## Software development {.cv-table .nohead .vertical-top}
```{r}
cv_entries %>% 
  filter(type == 'programming') %>% 
  replace_na(list(where = "", additional_info = "")) %>% 
  mutate(what = str_c(what, ", ", where, "<br>", additional_info)) %>% 
  select(year_begin, what) %>% 
  arrange(desc(year_begin)) %>% 
  kable(align = c('l', 'l'))
```

## Skills {.technical .nohead}
```{r}
cv_entries %>% 
  filter(type == 'technical') %>% 
  mutate(what = str_c("• ", what, " ", additional_info)) %>% 
  select(type, what) %>% 
  mutate(type = "") %>% 
  kable()
```


# Personal
## Skills & volunteering {.personal .service .nohead}
```{r}
cv_entries %>%
  filter(type == 'volunteering') %>%
  mutate(what = str_c("<span class='work-title'>", what, "</span><br class='work-break'>", where)) %>%
  mutate(what = ifelse(!is.na(additional_info), str_c(what, "<br>", additional_info), what)) %>%
  mutate(year = ifelse(!is.na(year_end), str_c(year_begin, " --- ", year_end), year_begin)) %>%
  arrange(desc(year), desc(year_end)) %>%
  select(year, what) %>%
  kable()
```

  </div>
</div>
