---
title: "CV"
menu: main
editor_options: 
  chunk_output_type: inline
---


<!-- add a floating table of contents: https://afeld.github.io/bootstrap-toc/ -->
<div class="row cv-page">
<!-- sidebar, which will move to the top on a small screen -->
<div class="col-sm-2 cv-navbar"> 
<nav id="toc" data-toggle="toc" class="sticky-top"></nav>
</div>

<div class="col-sm-9 cv-entries">

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(tidyverse)
library(knitr)
library(here)
library(lubridate)
library(kableExtra)
library(DT)
library(glue)
 
#### publications #####
publications <- read_csv(here::here("data/publications.csv"))

#### all other entries #####
cv_entries <- read_csv(here::here("data/cv_entries.csv")) %>% 
  mutate(year_begin = year(date)) %>%
  mutate(year_end = case_when(
    date_end == "present" ~ date_end,
    !is.na(date_end) ~ str_sub(date_end, 1, 4),
    is.na(date_end) ~ date_end
  )) %>%
  mutate(year = ifelse((is.na(year_end) | year_begin == year_end),
                      year_begin,
                      str_c(year_begin, " --- ", year_end)))


blank_year_when_repeated <- function(cv_entry_tibble){
  cv_entry_tibble %>% 
    mutate(row_number = row_number()) %>% 
    mutate(year_begin = as.character(year_begin),
           year_begin = case_when(
             row_number == 1 ~ year_begin,
             year_begin == lag(year_begin) ~ str_c('<span class="repeated-year">', year_begin, '</span>'),
             year_begin != lag(year_begin) ~ year_begin
           )) %>% 
    mutate(year = if_else(!is.na(lag(year)) & lag(year) == year, 
                          str_c('<span class="repeated-year">', year, '</span>'),
                          year))
}
```


```{css}
.repeated-year {
  color: white;
}
```


# Summary

I am passionate about using insights from the behavioural neurosciences to **design digital technology that is sensitive to human limitations and biases**, particularly in relation to attention and self-regulation.

My **academic and professional background** is highly interdisciplinary, and I try to integrate best practices from many work spheres, such as using tools from large-scale event management to structure academic projects.

My **personal interests** include backpacking, samatha meditation, dancing (Cuban salsa and swing), surfing, and playing music (often with my concept band the [Karaoke Collective](https://karaokecollective.com)).

<a class="btn btn-light" href="/pdfs/academic_cv.pdf" role="button"><i class="fa fa-download"></i> CV as PDF</a>

# Academia {.domain-header}
<h2 data-toc-text="Positions">Research positions</h2>
```{r}
cv_entries %>% 
  filter(type == 'research_positions', is.na(exclude)) %>%
  mutate(what = str_c("<span class='cv-entry-title'>", what, "</span><br>", 
                      where)) %>% 
  select(year, what) %>% 
  kable(escape = FALSE)

```

## Education
```{r}
cv_entries %>% 
  filter(type == 'education') %>% 
  mutate(what = str_c("<span class='cv-entry-title'>", what, "</span>, ", where,
                      "<br>", additional_info,
                      "<br>", additional_info2)) %>% 
  select(year, what) %>% 
  kable(escape = FALSE)

```

<h2 data-toc-text="Awards">Awards and honours</h2>
```{r}
cv_entries %>% 
  filter(type == 'awards') %>%
  filter(!(website == "n") | is.na(website)) %>% 
  mutate(what = if_else(
    !is.na(where),
    str_c("<span class='cv-entry-title'>", what, "</span>, ", where),
    str_c("<span class='cv-entry-title'>", what, "</span>"))
  ) %>% 
  blank_year_when_repeated() %>% 
  select(year_begin, what) %>% 
  kable(align = c("l", "l"), escape = FALSE)
```
 
<h2 data-toc-text="Grants">Major grants and funding</h2>
```{r}
cv_entries %>% 
  filter(type == 'major_grants',
         is.na(exclude)) %>%
  filter(!(website == "n") | is.na(website)) %>% 
  mutate(what = if_else(
    !is.na(additional_info),
    str_c("<span class='cv-entry-title'>", what, "</span>, ", where, "<br>", additional_info),
    str_c("<span class='cv-entry-title'>", what, "</span>, ", where))
  ) %>% 
  mutate(year_end = if_else(is.na(year_end), as.character(year_begin), year_end)) %>% 
  arrange(desc(year_end)) %>% 
  blank_year_when_repeated() %>% 
  select(year, what) %>% 
  kable(align = c("l", "l"), escape = FALSE) 
```


<h2 data-toc-text="Dissemination">Research dissemination</h2>

<!-- Nav tabs -->
<ul class="nav nav-tabs" id="dissemination-tab">
<li class="nav-item">
<a class="nav-link active" data-toggle="tab" href="#talks">Talks</a>
</li>
<li class="nav-item">
<a class="nav-link" data-toggle="tab" href="#posters">Posters</a>
</li>
<li class="nav-item">
<a class="nav-link" data-toggle="tab" href="#media">Media</a>
</li>
</ul>

```{r create-tables}
talks_table <- cv_entries %>% 
  filter(str_detect(type, 'talk')) %>%
  # replace markdown hyperlink syntax w/ html
  mutate(across(what:additional_info, ~str_replace(., "\\[([^]]*)\\]\\(([^\\s^\\)]*)[\\s\\)]", "<a href='\\2'>\\1</a>"))) %>% 
  mutate(what_translation = ifelse(!is.na(what_translation), str_c("(", what_translation, ")"), what_translation)) %>% 
  replace_na(list(institution = "", 
                  department = "", 
                  where = "", 
                  what_translation = "")) %>% 
  mutate(where = ifelse(where != "" & institution != "", str_c(", ", where), where),
         department = ifelse(department != "", str_c(", ", department), department),
         slides = ifelse(!is.na(slides), str_c("<a href=", slides, ">Slides</a>"), ""),
         video = ifelse(!is.na(video), str_c("<a href=", video, ">Video</a>"), ""),
         conditional_break = ifelse(!is.na(slides) | !is.na(video), "<br>", "")) %>%
  mutate(additional_info = if_else(!is.na(additional_info), str_c(", ", additional_info), "")) %>% 
  mutate(what = str_c("<p><span class='cv-entry-title'>", 
                      institution,
                      where,
                      "</span>",
                      department, 
                      additional_info,
                      "</p><p class='talk-title'>", what, "<span class='talk-translation'> ", what_translation, "</span>",
                      conditional_break,
                      slides,
                      video,
                      "</p>"
                      )) %>%   
  mutate(date = as_date(date)) %>% 
  arrange(desc(date)) %>% 
  mutate(month = month(date, label = TRUE)) %>% 
  blank_year_when_repeated() %>% 
  select(year_begin, month, what)


poster_table <- cv_entries %>%  
  filter(type == 'poster') %>%
  mutate(across(institution:where, ~str_replace(., "\\[([^]]*)\\]\\(([^\\s^\\)]*)[\\s\\)]", "<a href='\\2'>\\1</a>"))) %>% 
  mutate(what_translation = ifelse(!is.na(what_translation), str_c("(", what_translation, ")"), what_translation)) %>% 
  replace_na(list(institution = "", 
                  department = "", 
                  where = "", 
                  what_translation = "")) %>% 
  mutate(where = ifelse(where != "" & institution != "", str_c(", ", where), where),
         department = ifelse(department != "", str_c(", ", department), department),
         slides = ifelse(!is.na(slides), str_c("<a href=", slides, ">Slides</a>"), ""),
         video = ifelse(!is.na(video), str_c("<a href=", video, ">Video</a>"), ""),
         conditional_break = ifelse(!is.na(slides) | !is.na(video), "<br>", "")) %>%
  mutate(what = str_c("<p><span class='cv-entry-title'>", 
                      institution,
                      where,
                      "</span>",
                      department, 
                      "</p><p class='talk-title'>", what, "<span class='talk-translation'> ", what_translation, "</span>",
                      conditional_break,
                      slides,
                      video,
                      "</p>"
                      )) %>%   
  select(year_begin, what) %>% 
  arrange(desc(year_begin))


media_table <- cv_entries %>% 
  filter(type == 'media') %>%
  mutate(what = glue("<span class='cv-entry-title'>{where}</span>, {what}")) |>
  mutate(year_begin = year(date)) %>% 
  select(year_begin, what)

```


```{r results='asis'}
# Tab panes
cat('<div class="tab-content">')

# talks tab
cat('<div class="tab-pane container active" id="talks">')
talks_table %>% 
  datatable(elementId = "talks-table-dt", 
            rownames = FALSE, 
            escape = FALSE, 
            class = 'row-border', 
            options = list(lengthMenu = list(c(10, -1), c("10", "All")))
            )

cat('</div>')

# posters tab
cat('<div class="tab-pane container fade" id="posters">')
poster_table %>% kable(align = c("l", "l"), escape = FALSE)
cat('</div>')

# media tab
cat('<div class="tab-pane container fade" id="media">')
media_table %>% kable(align = c("l", "l"), escape = FALSE)
cat('</div>')

cat('</div>') 
```




<h2 data-toc-text="Teaching">Teaching experience</h2>
<!-- ## Teaching experience -->
```{r}
cv_entries %>% 
  filter(type == 'teaching') %>% 
  mutate(what = ifelse(!is.na(additional_info), 
    str_c("<span class='cv-entry-title'>", what, "</span><br class='work-break'>", where, "<br>", additional_info),
    str_c("<span class='cv-entry-title'>", what, "</span><br class='work-break'>", where))) %>% 
  select(year, what) %>% 
  kable(escape = FALSE)
  
```

## Service
```{r}
cv_entries %>% 
  filter(type == 'service') %>% 
  mutate(where = ifelse(!is.na(url), str_c("[", where, "](", url, ")"), where)) %>% 
  mutate(what = ifelse(!is.na(additional_info),
                       str_c("<span class='cv-entry-title'>", what,
                      "</span><br class='work-break'>", 
                      where),
                      str_c("<span class='cv-entry-title'>", what,
                      "</span><br class='work-break'>", 
                      where))) %>% 
  arrange(desc(date_end), desc(date)) %>% 
  select(year, what) %>% 
  kable(escape = FALSE)

```


# Work
<h2 data-toc-text="Employments">Selected employments</h2>
```{r}
cv_entries %>% 
  filter(type == 'work', is.na(website)) %>% 
  mutate(additional_info = replace_na(additional_info, "")) %>% 
  mutate(what = str_c("<span class='cv-entry-title'>", what, "</span><br class='work-break'>", where, "<br>", additional_info)) %>% 
  arrange(desc(date)) %>% 
  select(year, what) %>% 
  kable(escape = FALSE)
```

<h2 data-toc-text="Development">Professional development</h2>
```{r}
cv_entries %>% 
  filter(type == 'prof-dev') %>% 
  mutate(what = str_c("<span class='cv-entry-title'>", what, "</span>, ", where)) %>% 
  select(year_begin, what) %>% 
  kable(align = c("l", "l"), escape = FALSE)
```

# Technical
## Skills
```{r}
cv_entries %>% 
  filter(type == 'technical') %>% 
  mutate(icon = case_when(
    str_detect(what, "data analysis") ~ "fa-bar-chart",
    str_detect(what, "research") ~ "fa-flask",
    str_detect(what, "Web") ~ "fa-laptop"
  )) %>% 
  mutate(what = str_c("<i class='fa fa-lg ", icon, "'></i> &nbsp;<span class='cv-entry-title'>", what, "</span> ", additional_info)) %>% 
  select(type, what) %>% 
  mutate(type = "") %>% 
  kable(escape=FALSE)
```

## R packages
```{r}
cv_entries %>% 
  filter(type == 'software-rstats' & is.na(exclude)) %>% 
  replace_na(list(where = "", additional_info = "")) %>% 
  mutate(what = glue("<span class='cv-entry-title'>{what}</span>, {where}")) %>%
  arrange(desc(year)) %>% 
  mutate(row_number = row_number()) %>% 
  select(year, what) %>% 
  kable(escape=FALSE)
```

## Apps
```{r}
cv_entries %>% 
  filter(type == 'software-browser-extensions' & is.na(exclude)) %>% 
  replace_na(list(where = "", additional_info = "")) %>% 
  mutate(what = glue("<span class='cv-entry-title'>{what}</span>, {where}")) %>%
  arrange(desc(year)) %>% 
  mutate(row_number = row_number()) %>% 
  select(year, what) %>% 
  kable(escape=FALSE)
```


# Personal
## Skills & volunteering
```{r}
cv_entries %>%
  filter(type == 'volunteering') %>%
  mutate(what = str_c("<span class='cv-entry-title'>", what, "</span><br class='work-break'>", where)) %>%
  mutate(what = ifelse(!is.na(additional_info), str_c(what, "<br>", additional_info), what)) %>%
  arrange(desc(date_end)) %>% 
  select(year, what) %>%
  kable(escape = FALSE) 
```

</div>

<div class="col-sm-1"></div>

</div>
